Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
typo

Within the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications, successes in various machine learning challenges
(\emph{e.g.} Kaggle), or significant statistics derived from our repositories
and mailing lists.  At the time of writing, the project is watched by 1309
people and forked 667 time on GitHub, and the mailing-list receives 300 mails
per month.
The version control logs for the development version of scikit-learn
% ddaa494c116e3c16bf032003c5cccbed851733d2
show 183 contributors to the project's source code and documentation
(after manual deduplication).

@@

At each point in this grid, $k$-fold cross validation is run
to estimate the performance of the estimator according to some measure
(e.g.\ accuracy, $F_\beta$-score or a host of clustering quality metrics)
and the best performing set of hyperparameters is stored
on the \texttt{GridSearchCV} object, again, as a public attribute.

>>>>

Within the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications, successes in various machine learning challenges
(e.g., Kaggle), or significant statistics derived from our repositories
and mailing lists.  At the time of writing, the project is watched by 1309
people and forked 667 time on GitHub, and the mailing-list receives 300 mails
per month.
The version control logs for the development version of scikit-learn
% ddaa494c116e3c16bf032003c5cccbed851733d2
show 183 contributors to the project's source code and documentation
(after manual deduplication).

@@

At each point in this grid, $k$-fold cross validation is run
to estimate the performance of the estimator according to some measure
(e.g., accuracy, $F_\beta$-score or a host of clustering quality metrics)
and the best performing set of hyperparameters is stored
on the \texttt{GridSearchCV} object, again, as a public attribute.
